flowCore: data structures pacakge for flow cytometry data

### 2007-04-05 inst/doc/HowTo-flowCore.Rnw
work on man page still warnings for summary methods and %&%
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@23624 bc3139a8-67e5-0310-9ffc-ced21a209358

\title{flowCore: data structures for flow cytometry data}
\author{N. Le Meur F. Hahne B. Ellis P. Haaland}

@@

\subsection{flowFrame}
The objects of class \Robject{flowFrame} are the containers for storing individual 
cytometry measurements originated from one FCS file. \\
%%need description of the slots and maybe methods associated

\subsection{flowSet}
An flow cytometry experiment usually include several sample and several measurements. 
A data structure is thus needed to store those collections of measurements.  
The package \Rpackage{flowCore} stores the measurement and the associated data 
information in objects of class \Robject{flowSet}. 
A \Robject{flowSet} object contains two main slots \Robject{exprs}, an environment data structure 
that stores the flow cytometry measurements and the \Robject{phenoData}. The \Robject{phenoData} slot 
contains all the relevant experiment-wide meta-data, \textit{e.g.} 
phenotypic and experimental information relevant to the management and/or the analysis of the data.\\

@@

\subsection{Transformation}
While analyzing flow cytometry data, various parameter transformations are performed 
to provide user-friendly visualization and/or to perform statistical analyses and interpret the data. 
Following the standard \cite{Spidlen2006} 8 transformations are pre-defined: linear, quadratic, natural logarithm, 
logarithm (with a specified base), hyperlog, bi-exponential, logicle, and split-scale.\\

%%Can we define other?   
%%can be applied when reading in the data.

\subsection{Filter}
The role of filtering strategies are to identify and characterize diffrent cells population in sample.
%% Filtering vs Gating
%%Byron's vignette?
%%several approach from basic to DAG ...\\

>>>>

\title{flowCore: data structures pacakge for flow cytometry data}
\author{N. Le Meur F. Hahne B. Ellis P. Haaland}

@@

\subsection{flowFrame}
The objects of class \Robject{flowFrame} are the containers for storing individual 
cytometry measurements originated from one FCS file. The information available are:\\
%%need description of the slots and maybe methods associated
\begin{itemize}
\item exprs, containing the measured intensities. Rows correspond to cells, columns to the
      different channels. 
\item parameters, containing information about each column of the  flowFrame. This will generally
      be filled in by \Rfunction{read.FCS} or similar functions using data from
      the \Robject{description} slot that describes the parameters.
\item description is list containing the meta data included in the FCS file.
\end{itemize}

\subsection{flowSet}
An flow cytometry experiment usually include several sample and several measurements. 
A data structure is thus needed to store those collections of measurements.  
The package \Rpackage{flowCore} stores the measurement and the associated data 
information in objects of class \Robject{flowSet}, a collection of \Robject{flowFrame}. 
A \Robject{flowSet} object contains two main slots \Robject{frames}, an environment data structure 
that stores the flow cytometry measurements as \Robject{flowFrame} and the \Robject{phenoData}. 
The \Robject{phenoData} slot contains all the relevant experiment-wide meta-data, \textit{e.g.} 
phenotypic and experimental information relevant to the management and/or the analysis of the data.\\

@@

\subsection{Transformation}
While analyzing flow cytometry data, various parameter transformations are performed 
to provide user-friendly visualization and/or to perform statistical analyses and interpret the data. 
The proposed standard \cite{Spidlen2006} defined 8 transformations communly used: linear, quadratic, natural logarithm, 
logarithm (with a specified base), hyperlog, bi-exponential, logicle, split-scale. All of them are 
implemented in \Rpackage{flowcore} and a few other have been added. Each transformation has specific properties:\\

%%could be a table
\begin{itemize}
\item linear
\item logarithm
\item biexponential
\item logicle transformation help to visualize cells with minimal fluorescence 
  (cells usually pilled up on the axis with logarithmic displays) \citep{Herzenberg2006}
\item arcsinh 
\end{itemize}

\subsection{Filter}
The role of filtering strategies are to identify and characterize different cells population in sample.
%% Filtering vs Gating
%%Byron's vignette?
%%several approach from basic to DAG ...\\
